---
title: "Intro to R Markdown"
author: "STAT 630, Eric Fox"
output: html_document
---

### Text and Lists

Markdown provides an easy way to make lists and format text.

* plain  
* **bold**
* *italics*
* `code`

Be sure to put a space after the * when you are creating bullets and a space after # when creating section headers.

### R Code Chunks

Code in R chunks will be printed an evaluated.

```{r}
summary(mtcars$mpg)
```

You can also use "chunk options" to modify how your R chunks work.  We can hide the code:

```{r, echo = FALSE}
summary(mtcars$mpg)
```

Or we can hide the output:

```{r, eval = FALSE}
summary(mtcars$mpg)
```

### Inline R Code

You can put R output directly into text, as in: the mean number of miles per gallon is  `r round(mean(mtcars$mpg), 2)`.

### Graphics

```{r}
plot(mtcars$wt, mtcars$mpg)
```

For better presentation adjust the chunk options `fig.width` and `fig.height`.

```{r, fig.width=4, fig.height=4}
plot(mtcars$wt, mtcars$mpg)
```

### Equations

LaTeX equations can be embedded in R Markdown documents.

Inline equation: $a^2 + b^2 = c^2$

Display equations:
$$\bar{x} = \frac{1}{n}\sum_{i=1}^n x_i = \frac{x_1 + x_2 + \cdots + x_n}{n}$$

### Destination Formats

This file can be knit to HTML, PDF, or Word.  In RStudio, just select the desired 
output file type and click on `Knit HTML`, `Knit PDF`, or `Knit Word`.  You will need LaTeX installed to knit to PDF.  

Note that Blackboard does not accept HTML files.  One workaround is to first zip your HTML file, and then submit the zipped file to Blackboard.

### Links

Some helpful links for learning R Markdown:

* [Markdown Basics](https://rmarkdown.rstudio.com/authoring_basics.html)
* [Lessons from RStudio](https://rmarkdown.rstudio.com/lesson-1.html)
* [Youtube tutorial by Dr. Roger Peng](https://www.youtube.com/watch?v=DNS7i2m4sB0&t=328s)





